Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-20 paper.tex
save

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual. Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs ${\cal C} = \{ (a, s) \in
{\cal A} \times {\cal S} \}$, each indicating that signature $s$ is known with high confidence
to belong to individual $a$. Equivalently, ${\cal C}$ can be seen as a set of partial
clusters $c_a$, each including all signatures $s$ for which $(s, a) \in {\cal C}$.

@@

To form flat clusters out of the hierarchy, one must decide on a maximum
distance threshold above which clusters are considered to correspond to
distinct authors.  Exploiting knowledge from the partial clusters known in
${\cal C}$, we evaluate three cut-off strategies:
\begin{itemize}
\item \textit{No cut:} all signatures from the same block are assumed to be from the same author.
\item \textit{Global cut:} the threshold is chosen globally over all blocks, as the one maximizing some score $f({\cal C}, \hat{{\cal C}}_t)$.
\item \textit{Block cut:} the threshold is chosen locally at each block $b$, as the one maximizing some score $f({\cal C}^b, \hat{{\cal C}}^b_t)$. In case ${\cal C}^b$ is empty, then
                 all signatures from $b$ are clustered together.
\end{itemize}
Where $\hat{{\cal C}}_t$ denotes the predicted clusters, restricted to the
signatures in ${\cal C}$, when cutting the hierarchy at threshold $t$, and
where ${\cal C}^b$ is the subset of ${\cal C}$ including only those signatures
from block $b$.

>>>>

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual (without knowing who). Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs ${\cal C} = \{ (a, s) \in
{\cal A} \times {\cal S} \}$, each indicating that signature $s$ is known with high confidence
to belong to individual $a$. Equivalently, ${\cal C}$ can be seen as a set of partial
clusters $c_a$, each including all signatures $s$ for which $(s, a) \in {\cal C}$. \glnote{Change notations for ${\cal C}$!!}

@@

To form flat clusters out of the hierarchy, one must decide on a maximum
distance threshold above which clusters are considered to correspond to
distinct authors.  Exploiting knowledge from the partial clusters known in
${\cal C}$, we evaluate the following semi-supervised cut-off strategies:
\begin{itemize}
\item \textit{No cut:} all signatures from the same block are assumed to be from the same author.
\item \textit{Global cut:} the threshold is chosen globally over all blocks, as the one maximizing some score $f({\cal C}, \hat{{\cal C}}_t)$.
\item \textit{Block cut:} the threshold is chosen locally at each block $b$, as the one maximizing some score $f({\cal C}^b, \hat{{\cal C}}^b_t)$. In case ${\cal C}^b$ is empty, then
                 all signatures from $b$ are clustered together.
\end{itemize}
Where $\hat{{\cal C}}_t$ denotes the predicted clusters, restricted to the
signatures in ${\cal C}$, when cutting the hierarchy at threshold $t$, and
where ${\cal C}^b$ is the subset of ${\cal C}$ including only those signatures
from block $b$.
